---
title: "Status honor and demographics"
author: "Joseph"
date: "2/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Preparation

```{r setup, include=FALSE}
library(hablar) #you need this for bat ch-converting to numeric
library(tidyverse)
library(forcats) #for reordering factors
library(shiny)

grudata <- read_csv("data/transdata.csv")

```

# Data cleaning

```{r}
grudata <- grudata %>%
  slice(-1, -2) %>% #remove first and second row (irrelevant column titles)
  dplyr::filter(Status==0) %>% #remove survey previews
  dplyr::filter(Finished==1) %>% #remove unfinished responses
  retype() #guesses the right data type then auto-converts

column1 <- grudata %>% 
  select(starts_with("desc_wrds_1")) %>% 
  count()

names(grudata)

```

# Demographic Breakdown

```{r}
grudata %>% 
  dplyr::select("demog_yr") %>% 
  convert(num(demog_yr)) %>% 
  mutate(age = 2021 - demog_yr) %>% 
  summarize(mean_age = mean(age, na.rm = T),
            sd_age = sd(age, na.rm = T))

age <- grudata %>% 
  dplyr::select("demog_yr") %>% 
  convert(num(demog_yr)) %>% 
  mutate(age = 2021 - demog_yr) %>% 
  drop_na()

range(age$age)

grudata %>% 
  dplyr::select("demog_sex") %>% 
  count() %>% 
  mutate(gender = ifelse(demog_sex == 1, "male",
                         ifelse(demog_sex == 2, "female", 
                                ifelse(demog_sex == 3, "other",
                                       ifelse(demog_sex == 4, "prefer_not", "blank"))))) %>% 
  relocate(gender, .before = freq) %>% 
  mutate(prop = round(freq/sum(freq), 2))


```


# Honor Composite Score

```{r}
df.honor <- grudata %>% 
  dplyr::select(ResponseId, starts_with("honor")) %>% 
  rowwise() %>%  
  dplyr::mutate(honor_composite = round(mean(c(honor_respect, honor_disres, honor_socialimage, 
                                  honor_careimplicatio, honor_defendfam, na.rm = T)), 2)) %>% #avg 5 scales
  dplyr::select(ResponseId, honor_composite)

df.honor %>% 
  print(10) #see first 10 rows


```

# Status Wrangling and Analysis

## Status Ratings

```{r}
grudata %>% 
  dplyr::select(ResponseId, starts_with("stat-tar.US")) %>% 
  print(10)


df.status <- grudata %>% 
  dplyr::select(ResponseId, starts_with("stat")) %>% #select status rating columns
  drop_na() %>% 
  pivot_longer(cols = -ResponseId,
               names_to = c("status2", "rating"),
               names_sep = "_",
               values_to = "values",
               values_transform = list(values = as.character)) %>% #make long
  convert(num(rating)) %>% 
  filter(values == "On") %>% 
  separate(status2, c("variable", "evaluated"), "-") %>% 
  select(-variable, -values) %>% #deselect variable (list of 'stat') and values (list of 'On')
  drop_na(rating) %>% 
  pivot_wider(names_from = "evaluated",
              values_from = "rating")

df.status %>% 
  print(10)
```

## Status Exploratory Analyses

```{r}
# Show table with group means
df.status %>% 
  pivot_longer(cols = -ResponseId,
               names_to = "evaluatee",
               values_to = "ratings") %>% 
  group_by(evaluatee) %>% 
  dplyr::summarize(mean_rating = mean(ratings, na.rm = T))

#Visualize group means
df.status %>% 
  pivot_longer(cols = -ResponseId,
               names_to = "evaluatee",
               values_to = "ratings") %>% 
  dplyr::mutate(across(.cols = "evaluatee",
                       .fns = ~as.factor(.))) %>% 
  dplyr::mutate(Evaluatee = fct_relevel(evaluatee, "self.US", "tar.US", "self.comm", "tar.comm")) %>% 
  select(-evaluatee) %>% 
  relocate(ratings,  .after = Evaluatee) %>% 
  separate("Evaluatee", c("object", "region")) %>% #separate columns for easier plotting
  ggplot(aes(x = object,
             y = ratings)) +
  stat_summary(fun.y = "mean",
               geom = "point") +
  # stat_summary(fun.data = "mean_cl_boot",   
  #              geom = "linerange") +
  facet_wrap(~region) +#NB: after adding C.Intervals, there doesn't seem to be any group differences +
  labs(title = "Status ratings of self and target in the US and community")

```

## Status vs Honor Values Scale

Results: Not hypothesis-tested yet, but the trend appears to be that individuals with higher honor scores held grudges on targets of a higher status than them, whereas individuals with lower honor scores held grudges on targets of a lower status than themself

```{r}
df.honstat <- df.status %>% #combine status and honor values
  left_join(df.honor %>% 
              select(ResponseId, honor_composite),
            by = "ResponseId") %>% 
  drop_na()

#maybe plot honor against difference between target and self evaluations. Get mean target and mean Self
df.honstat %>% 
  rowwise() %>% 
  dplyr::mutate(tar.mean = mean(c(tar.US, tar.comm)),
                self.mean = mean(c(self.US, self.comm)),
                diff = tar.mean - self.mean) %>% 
  ggplot(aes(x = honor_composite,
             y = diff)) +
  geom_point() +
  geom_smooth(method = "lm", se = T) +
  geom_hline(yintercept = 0, 
             linetype = 2, 
             color = "dark grey") +
  labs(y = "Target - Self status rating",
       x = "Honor values score")


df.honstat %>% 
  rowwise() %>% 
  dplyr::mutate(tar.mean = mean(c(tar.US, tar.comm)),
                self.mean = mean(c(self.US, self.comm)),
                diff = tar.mean - self.mean) %>% 
  ggplot(aes(x = honor_composite,
             y = tar.mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = T) +
  geom_hline(yintercept = 0, 
             linetype = 2, 
             color = "dark grey") +
  labs(y = "Target status rating",
       x = "Honor values score")


df.honstat %>% 
  rowwise() %>% 
  dplyr::mutate(tar.mean = mean(c(tar.US, tar.comm)),
                self.mean = mean(c(self.US, self.comm)),
                diff = tar.mean - self.mean) %>% 
  ggplot(aes(x = honor_composite,
             y = self.mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = T) +
  geom_hline(yintercept = 0, 
             linetype = 2, 
             color = "dark grey") +
  labs(y = "Self status rating",
       x = "Honor values score")


```

## Demographics vs Honor & Status (political orientation, income)

```{r}


```

