---
title: "MFD analysis"
author: "Joseph"
date: "2/10/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(hablar)

grudata <- read_csv("data/transdata.csv")
#q1 
df.desc1a_mfd_norm <- read_csv("post_norm/q1_words/desc_1a_mfd_norm.csv")
df.desc1b_mfd_norm <- read_csv("post_norm/q1_words/desc_1b_mfd_norm.csv")
df.desc1c_mfd_norm <- read_csv("post_norm/q1_words/desc_1c_mfd_norm.csv")
df.desc1d_mfd_norm <- read_csv("post_norm/q1_words/desc_1d_mfd_norm.csv")
df.desc1e_mfd_norm <- read_csv("post_norm/q1_words/desc_1e_mfd_norm.csv")
#q2
df.descapp_mfd_norm <- read_csv("post_norm/q2_app/desc_app_mfd_norm.csv")
df.descinapp_mfd_norm <- read_csv("post_norm/q2_app/desc_inapp_mfd_norm.csv")

#q3
df.desc3_mfd_norm <- read_csv("post_norm/q3_rsn/desc_rsn_mfd_norm.csv")
#q4
df.emtn1a_mfd_norm <- read_csv("post_norm/q4_emtn/desc_emtn_1a_mfd_norm.csv")
df.emtn1b_mfd_norm <- read_csv("post_norm/q4_emtn/desc_emtn_1b_mfd_norm.csv")
df.emtn1c_mfd_norm <- read_csv("post_norm/q4_emtn/desc_emtn_1c_mfd_norm.csv")
df.emtn1d_mfd_norm <- read_csv("post_norm/q4_emtn/desc_emtn_1d_mfd_norm.csv")
df.emtn1e_mfd_norm <- read_csv("post_norm/q4_emtn/desc_emtn_1e_mfd_norm.csv")
#q5
df.crmst_mfd_norm <- read_csv("post_norm/q5_crmst/desc_crmst_mfd_norm.csv")

```

# Data cleaning

```{r}
grudata <- grudata %>%
  slice(-1, -2) %>% #remove first and second row (irrelevant column titles)
  dplyr::filter(Status==0) %>% #remove survey previews
  dplyr::filter(Finished==1) %>% #remove unfinished responses
  retype() #guesses the right data type then auto-converts

names(grudata)

```

# Define functions

Create functions to avoid repetition

```{r}
#Q1 AND Q4 FUNCTIONS ========================# 
# data wrangling function #
wrangle_norm_df <- function (df) {
  df %>% 
  dplyr::select(-Filename) %>% 
  pivot_longer(cols = everything(),
               names_to = "category",
               values_to = "response") %>%
  dplyr::filter(!category %in% c("Segment", "Dic"))
}

# table wrangling function#
wrangle_14_table <- function (df) {
  df %>% 
  group_by(category) %>% 
  dplyr::summarize(mean_mentions = mean(mentions)) %>% 
  dplyr::arrange(desc(mean_mentions)) %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()
}

# nth plotting function #
plot_nth <- function (df) {
  df %>% 
    separate(category, c("Number", "category"), "                    ") %>% #Spacing = 10 tabs!!
    ggplot(aes(x = position, y = mentions, group = category, color = category)) +
    geom_point() +
    labs(x = "nth response",
         y = "percent mentions",
         title = "Percent mentions in MFD dictionary categories") 
}

# mean plotting function #
plot_mean_mentions <- function (df) {
  df %>% 
  separate(category, c("Number", "category"), "                    ") %>% #Spacing = 10 tabs!!
  group_by(category) %>% 
  dplyr::summarize(mean_mentions = mean(mentions)) %>% 
  dplyr::arrange(desc(mean_mentions)) %>% 
  ggplot(aes(x = reorder(category, mean_mentions), y = mean_mentions, group = category, fill = category)) +
  geom_bar(stat = "identity") +
  labs(y = "mean mentions (percent)",
       title = "Q4 Percent mean mentions in MFD dictionary categories") +
  coord_flip() +
  theme(legend.position = "none")
 
}

# data wrangling function for combined #
wrangle_14_df <- function (df) {
  df %>% 
  separate(category, c("Number", "category"), "                    ") %>% #Spacing = 10 tabs!!
  group_by(category) %>% 
  dplyr::summarize(mentions = mean(mentions)) %>% 
  dplyr::arrange(desc(mentions)) 
}

#Q2, Q3 AND Q5 FUNCTIONS ========================# 
# table wrangling function #
wrangle_235_table <- function (df) {
  df %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("percent" = response) %>% 
  tibble::as_tibble() %>% 
  dplyr::arrange(desc(percent)) %>% 
  rmarkdown::paged_table()
}

# plotting function #
plot_235 <- function (df) {
  df %>% 
    wrangle_norm_df() %>% 
    dplyr::rename("mentions" = response) %>% 
    # dplyr::filter(!category %in% c("Segment", "Dic")) %>% 
    separate(category, c("Number", "category"), "                    ") %>% #Spacing = 10 tabs!!
    dplyr::arrange(desc(mentions)) %>% 
    ggplot(aes(x = category, y = mentions, group = category, fill = category)) +
    geom_bar(stat = "identity") +
    labs(y = "mentions (percent)",
         title = "Percent mean mentions in MFD dictionary categories") +
    coord_flip() +
    theme(legend.position = "none")  
}

#data wrangling function for combined #
wrangle_235_df <- function (df) {
  df %>% 
  dplyr::select(-Filename) %>% 
  pivot_longer(cols = everything(),
               names_to = "category",
               values_to = "mentions") %>%
  dplyr::filter(!category %in% c("Segment", "Dic")) %>% 
  separate(category, c("Number", "category"), "                    ") %>% #Spacing = 10 tabs!!
  dplyr::arrange(desc(mentions)) %>% 
  dplyr::select(-Number)
}

```


# Q1 Analysis

List some (5) words that come to mind when you think of holding a grudge

```{r}
#preview  rows
grudata %>%
  dplyr::select("desc_wrds_1", "desc_wrds_2", "desc_wrds_3", "desc_wrds_4", "desc_wrds_5") %>% 
  print(10) 

head(grudata)

# wrangle  #
df.desc1a_mfd_norm  <- df.desc1a_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_1" = response)

df.desc1b_mfd_norm <- df.desc1b_mfd_norm%>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_2" = response)

df.desc1c_mfd_norm <- df.desc1c_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_3" = response)

df.desc1d_mfd_norm <- df.desc1d_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_4" = response)

df.desc1e_mfd_norm <- df.desc1e_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_5" = response)

# Join # 
df.desc_1_mfd_all <- plyr::join_all(list(df.desc1a_mfd_norm, df.desc1b_mfd_norm ,
                                         df.desc1c_mfd_norm , df.desc1d_mfd_norm, df.desc1e_mfd_norm), 
                                    by='category', 
                                    type='left') %>% 
  # filter(categories %in% c("anger","adj")) %>%  ## ACTIVATE this to subset specific categories
  pivot_longer(cols = -category,
               names_to = "position",
               values_to = "mentions")

#Table showing mean mentions in most prominent categories # 
df.desc_1_mfd_all %>% 
  wrangle_14_table()

#plot nth #
df.desc_1_mfd_all %>% 
  plot_nth() +
  labs(title = "Q1 Percent mentions in MFD dictionary categories")

#plot mean mentions #
df.desc_1_mfd_all %>% 
  plot_mean_mentions() +
  labs(title = "Q1 Percent mean mentions in MFD dictionary categories")

```


# Q2a Analysis

Describe a circumstance where you think its right to hold a grudge

```{r}
# preview data #
grudata %>%
  select(starts_with("desc_app")) %>% 
  print(10)

# table showing most prominent categories #
df.descapp_mfd_norm %>%
  wrangle_235_table()

#plot mean mentions #
df.descapp_mfd_norm %>% 
  plot_235() +
  labs(title = "Q2a Percent mean mentions in MFD dictionary categories")

```

# Q2b Analysis

Describe a circumstance where you think its wrong to hold a grudge

```{r}
# preview data 
grudata %>%
  select(starts_with("desc_inapp")) %>% 
  print(10)

# table showing most prominent categories
df.descinapp_mfd_norm %>%
  wrangle_235_table()

# plot mean mentions
df.descinapp_mfd_norm %>% 
  plot_235() +
  labs(title = "Q2b Percent mean mentions in MFD dictionary categories")

```


# Q3 Analysis

For what reason do people typically hold grudges? 

```{r}
# preview data 
grudata %>%
  select(starts_with("desc_rsn")) %>% 
  print(10)

# table showing most prominent categories
df.desc3_mfd_norm %>% 
  wrangle_235_table()

# plot mean mentions
df.desc3_mfd_norm %>% 
  plot_235() +
  labs(title = "Q3 Percent mentions in MFD dictionary categories")

```

# Q4 Analysis 

List some (5) emotions you think people feel when they hold a grudge

(Also use emotion category dictionary)

```{r}
#wrangle ============= #
df.emtn1a_mfd_norm <- df.emtn1a_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_1" = response)

df.emtn1b_mfd_norm <- df.emtn1b_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_2" = response)

df.emtn1c_mfd_norm <- df.emtn1c_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_3" = response)

df.emtn1d_mfd_norm <- df.emtn1d_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_4" = response)

df.emtn1e_mfd_norm <- df.emtn1e_mfd_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_5" = response)

# Join ========================== # 
df.emtn_mfd_all <- plyr::join_all(list(df.emtn1a_mfd_norm, df.emtn1b_mfd_norm,
                                       df.emtn1c_mfd_norm, df.emtn1d_mfd_norm, df.emtn1e_mfd_norm), 
                                  by='category', 
                                  type='left') %>% 
  # filter(categories %in% c("anger","adj")) %>%  ## ACTIVATE this to subset specific categories
  pivot_longer(cols = -category,
               names_to = "position",
               values_to = "mentions") 

#table showing mean mentions in most prominent categories ================# 
df.emtn_mfd_all %>% 
  wrangle_14_table()

#plot nth response ============ #
df.emtn_mfd_all %>%
  plot_nth() +
  labs(title = "Q4 Percent mentions in MFD dictionary categories")

#plot mean mentions ======#
df.emtn_mfd_all %>% 
  plot_mean_mentions() +
  labs(title = "Q4 Percent mean mentions in MFD dictionary categories")

```

# Q5 Analysis

Describe a circumstance where you have held a grudge (sentences)

```{r}
#preview data =============#
grudata %>% 
  select(starts_with("desc_crmst")) %>% 
  print(10)
  
#Table showing most prominent categories
df.crmst_mfd_norm %>% 
  wrangle_235_table()

# Plotting mentions ========================== # 
df.crmst_mfd_norm %>% 
  plot_235() +
  labs(title = "Q5 Percent mean mentions in MFD dictionary categories")
```

# MFD across all 5 questions

```{r}

#wrangle q2, q3 qnd q5 ============== #
q2a <- df.descapp_mfd_norm %>% 
  wrangle_235_df() %>% 
  dplyr::rename("mentions_2a" = mentions)

q2b <- df.descapp_mfd_norm %>% 
  wrangle_235_df() %>% 
  dplyr::rename("mentions_2b" = mentions)

q3 <- df.descapp_mfd_norm %>% 
  wrangle_235_df() %>% 
  dplyr::rename("mentions_3" = mentions)

q5 <- df.descapp_mfd_norm %>% 
  wrangle_235_df() %>% 
  dplyr::rename("mentions_5" = mentions)

#wrangle q1 and q2 ============== #
q1 <- df.desc_1_mfd_all %>%
  wrangle_14_df() %>% 
  rename("mentions_1" = mentions)

q4 <- df.emtn_mfd_all %>% 
  wrangle_14_df() %>% 
  rename("mentions_4" = mentions)

# Joining ========================== # 
df.all <- plyr::join_all(list(q1, q2a, q2b, q3, q4, q5), 
         by='category', 
         type='left')

df.all %>% 
  pivot_longer(cols = -category,
               names_to = "names",
               values_to = "mentions") %>%
  separate(names, c("names", "question"), "_") %>% 
  ggplot(aes(x = category, y = mentions, group = category, fill = category)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  coord_flip() +
  facet_wrap(~ question) +
  labs(y = "mentions(percent)",
       title = "Percent mentions of MFD categories across all 5 questions")

```

