---
title: "extra code"
author: "Joseph"
date: "1/21/2021"
output: html_document
---

```{r setup, include=FALSE}

 d[is.na(d)] <- 0
  
df %>% 
  add_column(new_col = NA, .after = "value") %>% 
  mutate_all(funs(ifelse(is.na(.), 0, .))) %>% 
  group_by(anger) %>% 
  mutate(anger = sum(value))


#this is summary stats. Instead do the stats for each person

d %>% 
  group_by() #demographic variable
  dplyr::select(starts_with("honor")) %>% 
  mutate(across(.cols = everything(),
                .fns = list(Composite = mean), na.rm = TRUE,
                .names = "{col}_{fn}"
                ))
  
  
  

```

LIWC ANALYSIS PLAN

1. Convert first mentions to txt then feed LIWC then export to csv and back to R
2. Repeat for 2nd, 3rd, and 4th mentions. 


Language processing

```{r}
#convert to long form
d_long <- d %>% 
  dplyr::select(starts_with("desc_wrds")) %>%
  gather(key, value, na.rm = TRUE) 

#total counts in long form data
d_long %>% 
  count(value)

# Accounting for alternative spellings in count
anger_counts <- c("anger", "Anger", "angee", "Angry", "angry", "ANGRY", "always upset",
            "annoyance", "Annoyance", "ANNOYANCE", "annoyed", "Annoyed", "annoying") #'anger' string alternatives

d_long_2 <- dplyr::select(d_long, -key)

df <- sapply(d_long_2, function(x) { #counting each occurrence in entire data frame
  sapply(anger_counts, function(y) {
    sum(grepl(y, x))
  })
}) %>%
    as.data.frame() 

df2 <- sum(df$value)
anger < - c("anger")
data.frame(all_occurences = sum(df$value),
           word = c("anger"))


# NB: you can just use summarize on its own i.e. 

# summarize(height = mean(height, na.rm = T)), and you will get just a single value
#           n = n())

#create a vector of all words and use as batch input to count function. then output a df with counts of all words and all their alts

#this will take a while
# or take all values in column 1 (for desc 1 through 5) then convert to one large vector and save as counts. Delete repeated strings Then run sapply through it. 

```


# Q1 Absolute Counts LIWC

LIWC software appears to have 2 uses:   
- Analyze text: Measures % of words in a category/ dimension. I ran this analysis on LIWC but I didn't show it here because it didn't seem all that useful but we can definitely revisit. 
- Categorize text: indicate which categories words belong to based on pre-defined categories. No ways to custom-make your own categories. This is the technique I used below. The word categories on LIWC are many and quite varied in their meaning. I just selected a subset here, and these can be subsetted further. Will explain more when we meet

List some (5) words that come to mind when you think of holding a grudge


```{r}
# 1 ==================  
df.desc_1 <- grudata %>% 
  select(starts_with("desc_wrds_1")) #first select columns
# write_csv(df.desc_1, "desc_1.csv") #then write to csv                    
# >Then open and convert to txt > Then categorize on LIWC
# > Then save LIWC txt output as csv > Then Read the saved csv back to R 
 
# 2 ================== 
df.desc_2 <- grudata %>% 
  select(starts_with("desc_wrds_2")) #first select columns
# write_csv(df.desc_2, "desc_2.csv") #then write to csv

# 3 ================== 
df.desc_3 <- grudata %>% 
  select(starts_with("desc_wrds_3")) #first select columns
# write_csv(df.desc_3, "desc_3.csv") #then write to csv

# 4 ================== 
df.desc_4 <- grudata %>% 
  select(starts_with("desc_wrds_4")) #first select columns
# write_csv(df.desc_4, "desc_4.csv") #then write to csv

# 5 ================== 
df.desc_5 <- grudata %>% 
  select(starts_with("desc_wrds_5")) #first select columns
# write_csv(df.desc_5, "desc_5.csv") #then write to csv
```


```{r}
## ================================================================== ##

df.desc1_cat <- df.desc1_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% #at this point we're more interested in categories than the words
  dplyr::summarize(n_1 = n())

df.desc2_cat <- df.desc2_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% #at this point we're more interested in categories than the words
  dplyr::summarize(n_2 = n())

df.desc3_cat <- df.desc3_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% #at this point we're more interested in categories than the words
  dplyr::summarize(n_3 = n())

df.desc4_cat <- df.desc4_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% #at this point we're more interested in categories than the words
  dplyr::summarize(n_4 = n())

df.desc5_cat <- df.desc5_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% #at this point we're more interested in categories than the words
  dplyr::summarize(n_5 = n())

# Joining ========================== # 
df.desc_all <- join_all(list(df.desc1_cat, df.desc2_cat, df.desc3_cat, df.desc4_cat, df.desc5_cat), 
         by='LIWC_categories', 
         type='left')

 # Plotting ========================== # 
df.desc_all %>% 
  #filter(categories %in% c("anger","adj")) %>%  ## ACTIVATE this to subset specific categories
  pivot_longer(cols = -LIWC_categories,
               names_to = "position",
               values_to = "mentions") %>% 
  filter(mentions > 20) %>% 
  ggplot(aes(x = position, y = mentions, group = LIWC_categories, color = LIWC_categories)) +
  geom_point() +
 #  geom_smooth(method = "lm", se = F)
  labs(x = "nth response",
       y = "total mentions",
       title = "Graph of total word mentions in selected LIWC categories")

# affect, negative emotion, anger, drives, verb (delete verb)
  
```

Q3 ANALYSIS - WHAT REASON DO PEOPLE TYPICALLY HOLD GRUDGES 

```{r}


### old ======#

# 

reason <- grudata %>% 
  select(starts_with("desc_rsn"))

reason_categorized <- reason_categorized %>% 
  slice(-1, -2) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% #at this point we're more interested in categories than the words
  dplyr::summarize(n_1 = n())

 # Plotting ========================== # 
reason_categorized %>% 
  #filter(categories %in% c("anger","adj")) %>%  ## ACTIVATE this to subset specific categories
  pivot_longer(cols = -LIWC_categories,
               names_to = "position",
               values_to = "mentions") %>% 
  ggplot(aes(x = position, y = mentions, group = LIWC_categories, color = LIWC_categories)) +
  geom_point() +
 #  geom_smooth(method = "lm", se = F)
  labs(x = "nth response",
       y = "total mentions",
       title = "Graph of total word mentions in selected LIWC categories")
  
```


Q4 OLD/ PREV ANALYSIS (I think this is counts)

```{r}


### OLD=================#
grudata %>% 
  select(starts_with("desc_emtn")) %>% 
  print(10)

# 1 ==================  
df.emtn_1 <- grudata %>% 
  select(starts_with("desc_emtn_1")) #first select columns
 write_csv(df.emtn_1, "emtn_1.csv") #then write to csv                    
# >Then open and convert to txt > Then categorize on LIWC
# > Then save LIWC txt output as csv > Then Read the saved csv back to R 

# 2 ================== 
df.emtn_2 <- grudata %>% 
  select(starts_with("desc_emtn_2")) #first select columns
# write_csv(df.emtn_2, "emtn_2.csv") #then write to csv

# 3 ================== 
df.emtn_3 <- grudata %>% 
  select(starts_with("desc_emtn_3")) #first select columns
# write_csv(df.emtn_3, "emtn_3.csv") #then write to csv

# 4 ================== 
df.emtn_4 <- grudata %>% 
  select(starts_with("desc_emtn_4")) #first select columns
# write_csv(df.emtn_4, "emtn_4.csv") #then write to csv

# 5 ================== 
df.emtn_5 <- grudata %>% 
  select(starts_with("desc_emtn_5")) #first select columns
# write_csv(df.emtn_5, "emtn_5.csv") #then write to csv

## ================================================================== ##

df.emtn1_cat %>% 
  print(10) #LIWC output


df.emtn1_cat <- df.emtn1_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% #at this point we're more interested in categories than the words
  dplyr::summarize(n_1 = n())

df.emtn2_cat <- df.emtn2_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% 
  dplyr::summarize(n_2 = n())

df.emtn3_cat <- df.emtn3_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% 
  dplyr::summarize(n_3 = n())

df.emtn4_cat <- df.emtn4_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% 
  dplyr::summarize(n_4 = n())

df.emtn5_cat <- df.emtn5_cat %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  group_by(LIWC_categories) %>% 
  dplyr::summarize(n_5 = n())

# Joining ========================== # 
df.emtn_all <- join_all(list(df.emtn1_cat, df.emtn2_cat, df.emtn3_cat, df.emtn4_cat, df.emtn5_cat), 
         by='LIWC_categories', 
         type='left')

df.emtn_all %>% 
  filter(categories %in% c("anger","adj")) %>%  ## ACTIVATE this to subset specific categories
  pivot_longer(cols = -LIWC_categories,
               names_to = "position",
               values_to = "mentions") %>% 
  ggplot(aes(x = position, y = mentions, group = LIWC_categories, color = LIWC_categories)) +
  geom_point() +
 #  geom_smooth(method = "lm", se = F)
  labs(x = "nth response",
       y = "total mentions",
       title = "Graph of total EMOTION word mentions in selected LIWC categories")
```

