---
title: "liwc_analysis_post"
author: "Joseph"
date: "2/23/2021"
output: html_document
---

Objective: To open up the blackbox of social, affective and cognitive categories that were flagged in analysis 1. We saw the % breakdown of words by category, now we are going to see what specific words were flagged in ecah category. 

```{r setup, include=FALSE}
library(hablar) #you need this for bat ch-converting to numeric
library(tidyverse)
library(forcats) #for reordering factors

grudata <- read_csv("data/transdata.csv")

```

Read text analysis files

```{r, include=FALSE}
#all normalized!
#q1 
df.desc1a_counts <- read_csv("post_analysis_counts/q1_words/desc_1a_counts.csv")
df.desc1b_counts <- read_csv("post_analysis_counts/q1_words/desc_1b_counts.csv")
df.desc1c_counts <- read_csv("post_analysis_counts/q1_words/desc_1c_counts.csv")
df.desc1d_counts <- read_csv("post_analysis_counts/q1_words/desc_1d_counts.csv")
df.desc1e_counts <- read_csv("post_analysis_counts/q1_words/desc_1e_counts.csv")

```

# Data cleaning

```{r}
grudata <- grudata %>%
  slice(-1, -2) %>% #remove first and second row (irrelevant column titles)
  dplyr::filter(Status==0) %>% #remove survey previews
  dplyr::filter(Finished==1) %>% #remove unfinished responses
  retype() #guesses the right data type then auto-converts

```

# Define functions

Create functions to avoid code repetition

```{r}
  
wrangle_counts_df <- function (df) {
  df %>% 
  slice(-1, -2, -3) %>% 
  pivot_longer(cols = -Word,
               names_to = "LIWC_categories",
               values_to = "check") %>% 
  drop_na() %>% 
  relocate(Word, .after = LIWC_categories) %>% 
  arrange(LIWC_categories)
}


```

# Q1 Analysis

List some (5) words that come to mind when you think of holding a grudge

This prompt would return associated concepts. Some could be specifically about grudges, but some could also be concepts that are different but closely related. I suppose this is a way to map out the coceptual distance with other concepts. 

```{r}
#wrangling
grudata %>%
  dplyr::select("desc_wrds_1", "desc_wrds_2", "desc_wrds_3", "desc_wrds_4", "desc_wrds_5") %>% 
  print(10) %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()

df.desc1a_counts <- df.desc1a_counts %>% 
  wrangle_counts_df()

```

## Affect

The positive dimensions are forgiveness (2), fairness (1), inspiration (1). Pride here means self-importance which is a negative trait

```{r}
df.desc1a_counts %>% 
  filter(LIWC_categories == "affect")

df.desc1a_counts %>% 
  filter(LIWC_categories == "posemo")

df.desc1a_counts %>% 
  filter(LIWC_categories == "negemo") %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()

df.desc1a_counts %>% 
  filter(LIWC_categories == "anx")

df.desc1a_counts %>% 
  filter(LIWC_categories == "anger") %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()

df.desc1a_counts %>% 
  filter(LIWC_categories == "sad")

```

## Social

```{r}

df.desc1a_counts %>% 
  filter(LIWC_categories == "social")

df.desc1a_counts %>% 
  filter(LIWC_categories == "family")

df.desc1a_counts %>% 
  filter(LIWC_categories == "friends")

df.desc1a_counts %>% 
  filter(LIWC_categories == "female")

df.desc1a_counts %>% 
  filter(LIWC_categories == "male")


```


## Cognitive Processes

```{r}

df.desc1a_counts %>% 
  filter(LIWC_categories == "cogproc")

df.desc1a_counts %>% 
  filter(LIWC_categories == "insight")

df.desc1a_counts %>% 
  filter(LIWC_categories == "cause") #Causal

df.desc1a_counts %>% 
  filter(LIWC_categories == "discrep") #Discrepancies

df.desc1a_counts %>% 
  filter(LIWC_categories == "tentat") #Tentative

df.desc1a_counts %>% 
  filter(LIWC_categories == "certain") #Certainty

df.desc1a_counts %>% 
  filter(LIWC_categories == "differ") #Differentiation

```



