---
title: "LIWC analysis"
author: "Joseph"
date: "1/15/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

NB: THIS ANALYSIS WILL ONLY DETECT SOCIAL, AFFECTIVE AND COGNITIVE CATEGORIES. REDO THE ANALYSIS WITH ALL CATEGORIES, NOW THAT I KNOW

Data Preparation

```{r setup, include=FALSE}
library(hablar) #you need this for bat ch-converting to numeric
library(tidyverse)
library(forcats) #for reordering factors

grudata <- read_csv("data/transdata.csv")

```

Read text analysis files

```{r, include=FALSE}
#all normalized!
#q1 
df.desc1a_norm <- read_csv("post_analysis_norm/q1_words/desc_1a_norm.csv")
df.desc1b_norm <- read_csv("post_analysis_norm/q1_words/desc_1b_norm.csv")
df.desc1c_norm <- read_csv("post_analysis_norm/q1_words/desc_1c_norm.csv")
df.desc1d_norm <- read_csv("post_analysis_norm/q1_words/desc_1d_norm.csv")
df.desc1e_norm <- read_csv("post_analysis_norm/q1_words/desc_1e_norm.csv")
#q2
df.descapp_norm <- read_csv("post_analysis_norm/q2_app/desc_app_norm.csv")
df.descinapp_norm <- read_csv("post_analysis_norm/q2_app/desc_inapp_norm.csv")
#q3
df.desc3_norm <- read_csv("post_analysis_norm/q3_rsn/desc_rsn_norm.csv")
#q4
df.emtn1a_norm <- read_csv("post_analysis_norm/q4_emtn/desc_emtn_1a_norm.csv")
df.emtn1b_norm <- read_csv("post_analysis_norm/q4_emtn/desc_emtn_1b_norm.csv")
df.emtn1c_norm <- read_csv("post_analysis_norm/q4_emtn/desc_emtn_1c_norm.csv")
df.emtn1d_norm <- read_csv("post_analysis_norm/q4_emtn/desc_emtn_1d_norm.csv")
df.emtn1e_norm <- read_csv("post_analysis_norm/q4_emtn/desc_emtn_1e_norm.csv")
#q5
df.crmst_norm <- read_csv("post_analysis_norm/q5_crmst/desc_crmst_norm.csv")

```


# Data cleaning

```{r}
grudata <- grudata %>%
  slice(-1, -2) %>% #remove first and second row (irrelevant column titles)
  dplyr::filter(Status==0) %>% #remove survey previews
  dplyr::filter(Finished==1) %>% #remove unfinished responses
  retype() #guesses the right data type then auto-converts

names(grudata)

```

# Q1 Analysis

List some (5) words that come to mind when you think of holding a grudge

```{r}
grudata %>%
  dplyr::select("desc_wrds_1", "desc_wrds_2", "desc_wrds_3", "desc_wrds_4", "desc_wrds_5") %>% 
  print(10) %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()

#create wrangling function ======== #
wrangle_norm_df <- function (df) {
  df %>% 
  dplyr::select(-Filename) %>% 
  pivot_longer(cols = everything(),
               names_to = "category",
               values_to = "response") %>%
  dplyr::filter(!category %in% c("Analytic", "Segment", "Dic", "Clout", "Authentic", "Tone")) %>% 
  dplyr::filter(response > 2.5) #arbitrary! Recheck
}

#call the function ============= #
df.desc1a_norm <- df.desc1a_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_1" = response)

df.desc1b_norm <- df.desc1b_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_2" = response)

df.desc1c_norm <- df.desc1c_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_3" = response)

df.desc1d_norm <- df.desc1d_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_4" = response)

df.desc1e_norm <- df.desc1e_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_5" = response)

# Joining ========================== # 
df.desc_1_all <- plyr::join_all(list(df.desc1a_norm, df.desc1b_norm, 
                                     df.desc1c_norm, df.desc1d_norm, df.desc1e_norm), 
                                by='category', 
                                type='left') %>% 
  # filter(categories %in% c("anger","adj")) %>%  ## ACTIVATE this to subset specific categories
  pivot_longer(cols = -category,
               names_to = "position",
               values_to = "mentions") 

#Table showing most prominent categories ================# 
df.desc_1_all %>% 
  group_by(category) %>% 
  dplyr::summarize(mean_mentions = mean(mentions)) %>% 
  dplyr::arrange(desc(mean_mentions)) %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()

# Plotting ========================== # 
df.desc_1_all %>% 
  ggplot(aes(x = position, y = mentions, group = category, color = category)) +
  geom_point() +
 #  geom_smooth(method = "lm", se = F)
  labs(x = "nth response",
       y = "percent mentions",
       title = "Percent mentions in LIWC dictionary categories")

```


# Q2a Analysis

Describe a circumstance where you think its right to hold a grudge


```{r}
#2a
#Preview data =============#
grudata %>%
  select(starts_with("desc_app")) %>% 
  print(10)

#Table showing most prominent categories
df.descapp_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("percent" = response) %>% 
  tibble::as_tibble() %>% 
  dplyr::arrange(desc(percent)) %>% 
  rmarkdown::paged_table()

```

# Q2b Analysis

Describe a circumstance where you think its wrong to hold a grudge

```{r}
#2b
#Preview data =============#
grudata %>%
  select(starts_with("desc_inapp")) %>% 
  print(10)

#Table showing most prominent categories
df.descinapp_norm %>% 
  dplyr::select(-Filename) %>% 
  pivot_longer(cols = everything(),
               names_to = "category",
               values_to = "percent") %>%
  dplyr::filter(!category %in% c("Analytic", "Segment", "Dic", "Clout", "Authentic", "Tone")) %>% 
  dplyr::filter(percent > 2.5) %>% #arbitrary! Recheck. Still 26 rows left!!
  dplyr::arrange(desc(percent)) %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()
```


# Q3 Analysis

For what reason do people typically hold grudges? 

```{r}
#Preview data =============+#
grudata %>%
  select(starts_with("desc_rsn")) %>% 
  print(10)

#Table showing most prominent categories =============+#
df.desc3_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("percent" = response) %>% 
  dplyr::arrange(desc(percent)) %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()

```



# Q4 Analysis 

List some (5) emotions you think people feel when they hold a grudge

```{r}
#Preview data =============#
grudata %>% 
  select(starts_with("desc_emtn")) %>% 
  print(10)

#call wrangling function ============= #
df.emtn1a_norm <- df.emtn1a_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_1" = response)

df.emtn1b_norm <- df.emtn1b_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_2" = response)

df.emtn1c_norm <- df.emtn1c_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_3" = response)

df.emtn1d_norm <- df.emtn1d_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_4" = response)

df.emtn1e_norm <- df.emtn1e_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("response_5" = response)

# Joining ========================== # 
df.emtn_all <- plyr::join_all(list(df.emtn1a_norm, df.emtn1b_norm, 
                                   df.emtn1c_norm, df.emtn1d_norm, df.emtn1e_norm), 
                              by='category', 
                              type='left') %>% 
  # filter(categories %in% c("anger","adj")) %>%  ## ACTIVATE this to subset specific categories
  pivot_longer(cols = -category,
               names_to = "position",
               values_to = "mentions") 

#Table showing most prominent categories ======= # 
df.emtn_all %>% 
  group_by(category) %>% 
  dplyr::summarize(mean_mentions = mean(mentions)) %>% 
  dplyr::arrange(desc(mean_mentions)) %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()

# Plotting ========================== # 
df.emtn_all %>% 
  ggplot(aes(x = position, y = mentions, group = category, color = category)) +
  geom_point() +
 #  geom_smooth(method = "lm", se = F)
  labs(x = "nth response",
       y = "percent mentions",
       title = "Percent mentions in LIWC dictionary categories")

```

# Q5 Analysis

Describe a circumstance where you have held a grudge (sentences)

```{r}
#Preview data =============#
grudata %>% 
  select(starts_with("desc_crmst")) %>% 
  print(10)
  
#Table showing most prominent categories
df.crmst_norm %>% 
  wrangle_norm_df() %>% 
  dplyr::rename("percent" = response) %>% 
  dplyr::arrange(desc(percent)) %>% 
  tibble::as_tibble() %>% 
  rmarkdown::paged_table()
```

